\textsf{Are large language models superhuman chemists?}

### 2024-10-17 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

\begin{itemize}
    \item \emph{End-to-end automation}. For model development, the evaluations must be run many times (e.g., on regular intervals of a training run).
    Approaches that rely on humans scoring the answers of a system\autocite{Schulze_Balhorn_2024, ai4science2023impact, castro2023large} can thus not be used.
    \item \emph{Careful validation by experts}. Manual curation is needed to minimize the number of incorrect or unanswerable questions.\autocite{northcutt2021pervasive}
    This is motivated by the observation that many widely used benchmarks are plagued by noisiness.\autocite{Frye_2023, Awg}
    \item \emph{Usable with models that support special treatment of molecules}. Some models, such as Galactica\autocite{taylor2022galactica}, use special tokenization or encoding procedures for molecules or equations.
    The benchmark system must encode the semantic meaning of various parts of the question or answer to support this.
    \item \emph{Usable with black box systems}. Many relevant systems do not provide access to model weights or raw logits.
    This might be the case because the systems are proprietary or because they involve not only \glspl{llm} but also external tools such as search \glspl{api} or code executors.\autocite{schick2024toolformer, karpas2022mrkl, yao2022react}
    Thus, a benchmark should not assume access to the raw model outputs but be able to operate on text completions.
    \item \emph{Probing capabilities beyond answering of \glspl{mcq}}. In real-world chemistry, as well as higher-level university education, multiple-choice questions are seldom utilized.
    Yet, most benchmarking frameworks focus on the \gls{mcq} setting because of the ease of evaluation. Realistic evaluations must measure capabilities beyond answering \gls{mcq}.
    \item \emph{Cover a diverse set of topics}. Chemistry, as the \enquote{central science}, bridges multiple disciplines.\autocite{Aspuru_Guzik_2018} To even just approximate \enquote{chemistry capabilities} the topics covered by a chemistry benchmark must be very diverse.
    \item \emph{Cover diverse skills}. To holistically judge performance it is important to cover questions relying on reasoning, calculation, knowledge, intuition. 
    \item \emph{Cover a range of difficulty levels}. To allow for a continuous measure of improvement for a range of different (evolving) systems, a benchmark should cover a wide range of difficulty levels.
    \item \emph{Impossible to completely solve with current models}. A benchmark should contain questions that are impossible to solve with current models. If current models can solve all questions, the benchmark provides no useful signal.
\end{itemize}

@@

% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/flesch_kincaid_reading_ease.pdf}
%     \caption{\textbf{Distribution of Flesch-Kincaid reading ease scores of the questions.} The Flesch-Kincaid reading ease score\autocite{flesch1948new} measures how easy a text is to read. It is calculated based on the average number of syllables per word and words per sentence. The higher the score, the easier the text is to read. The distribution of the questions' scores is shown in the histogram. }
%     \label{fig:flesch_kincaid_reading_ease}
%     \script{wordcloud.py}
% \end{figure}

\Cref{fig:question_count_barplot_mcq_vs_general} shows that most questions in our corpus are \gls{mcq}.
A substantial fraction, in contrast to other benchmarks, is open-ended. 
% \begin{figure}[htb]
%     \centering
%     \includegraphics{figures/question_count_barplot_mcq_vs_general.pdf}
%     \caption{\textbf{Number of multiple choice questions vs.\ open-ended questions per topic.} The bar plot shows the number of \gls{mcq} and general questions per topic.}
%     \label{fig:question_count_barplot_mcq_vs_general}
%     \script{plot_statistics.py}
% \end{figure}

@@

\subsection{Model performance}
We also evaluated the model performance on the entire \chembench corpus. 
\Cref{fig:barplot_all_correct_all_questions} shows the fraction of questions that were answered correctly by the models. 
Note that this ranking differs from the one on the \enquote{tiny} subset

@@

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{\textbf{Fraction of correctly answered questions per data source.} The heatmap shows, in color, the fraction of questions answered correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

% In addition, we analyzed the performance on questions which requires calculation. For this, we manually labeled questions that require multiple calculation steps. 
% We find that the ranking of models is different for questions with our without calculations (\Cref{fig:requires_cal}).

% \begin{figure}
%     \centering
%     \includegraphics{figures/model_overall_cal.pdf}
%     \caption{\textbf{Overall model performance for questions with and without calculation steps.} We find that the ranking of models changes if we evaluate them on questions that require and do not require calculations, respectively.}
%     \script{requires_calculation_plot.py}
%     \label{fig:requires_cal}
% \end{figure}

@@

% \begin{table}
%     \caption{\textbf{Spearman correlation coefficients for the correlation of model performance with molecular features.} The table shows the Spearman correlation coefficient $\rho$ for the correlation of the performance of the models with the number of atoms and the complexity of the molecules. }
%     \begin{tabularx}{\textwidth}{XXXX XXXX}
%         \toprule
%         topic & molecular descriptor & \(\rho\) GPT-4 & \(\rho \) Claude 3 & \( \rho \) Galactica &  \( \rho \) humans  \\ 
%         \midrule
%         number of \gls{nmr} signals & number of atoms &  \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_number_nmr_peaks.txt}  & \variable{output/correlation_correlation/spearman_num_atoms_human_is_number_nmr_peaks.txt} \\
%                               & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_number_nmr_peaks.txt} \\
%         \midrule 
%         total electron counts & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_electron_counts.txt} \\
%         \midrule 
%         \gls{smiles} \gls{iupac} name matching & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_name.txt} \\
%                 & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_name.txt} \\
%         \bottomrule
%     \end{tabularx}
%     \label{tab:correlation_coefficients}
% \end{table}

\subsection{Influence of model scale}
% To obtain first insights in how the performance \glspl{llm} depends on scale, we tested the \glspl{llm} of the LLaMA series. 
% Interestingly, we find that the 7B and 70B models perform comparably, with the 13B showing lower performance (fraction of correct answers for the 7B, 13B, and 70B models are \variable{output/llama/llama_7b.txt}, \variable{output/llama/llama_13b.txt}, \variable{output/llama/llama_70b.txt}).

% Note that such analyses are difficult as models are typically not directly comparable in terms of dataset and training protocol.\autocite{biderman2023pythia}
REWRITE.

\subsection{Human baseline}
\paragraph{App} To facilitate the collection of responses, we developed a responsive web application in Typescript using the Next.js\autocite{nextjs} app router framework.
This application handles serving the user interface and exposes various \gls{rest} \glspl{api} for relevant operations.
We utilize a Postgresql.
The web application is styled with Tailwind CSS\autocite{tailwindcss} using the shadcn/ui component library and uses NextAuth\autocite{nextauth} for easy and secure user authentication.
The application is hosted on the Vercel web hosting platform.

@@

We also recorded the time humans took to answer the questions. This time is the time from the question being displayed to the human to the human submitting the answer.
%Interestingly, we found no significant correlation between the experience of the human scorers and the performance on the questions (\Cref{fig:human_timing}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\)$\quad$, and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot, it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions. However, we see that human scorers typically took longer to correctly answer questions with tool use.}
    \label{fig:human_timing}
\end{figure}

Additionally, we prompted users to provide additional information about their experience in chemistry. 
While we recorded fine-grained information, e.g., their specialization, we focused on the number of years since the first university-level chemistry course.
\Cref{fig:experience_vs_correctness} shows that the experience of the human scorers was correlated with the correctness of their answers (\Cref{fig:experience_vs_correctness}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\), and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

\begin{figure}[htb]
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in the number of years since the first university-level chemistry course) of the human scorers wasp correlated with the correctness of their answers.}
    \label{fig:experience_vs_correctness}
\end{figure}

@@

% \begin{figure}[htb] 
%     \centering
%     \includegraphics{figures/confidence_score_distributions.pdf}
%     \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The bar plots show how many questions were answered with each confidence score.}
%     \label{fig:confidence_score_distributions}
%     \script{plot_confidence_score_distributions.py}
% \end{figure}

>>>>

\begin{itemize}
    \item \emph{End-to-end automation}. For model development, the evaluations must be run many times (e.g., on regular intervals of a training run).
    Approaches that rely on humans scoring the answers of a system\autocite{Schulze_Balhorn_2024, ai4science2023impact, castro2023large} can thus not be used.
    \item \emph{Careful validation by experts}. Manual curation is needed to minimize the number of incorrect or unanswerable questions.\autocite{northcutt2021pervasive}
    This is motivated by the observation that many widely used benchmarks are plagued by noisiness.\autocite{Frye_2023, Awg}
    \item \emph{Usable with models that support special treatment of molecules}. Some models, such as Galactica\autocite{taylor2022galactica}, use special tokenization or encoding procedures for molecules or equations.
    The benchmark system must encode the semantic meaning of various parts of the question or answer to support this.
    \item \emph{Usable with black box systems}. Many relevant systems do not provide access to model weights or raw logits.
    This might be the case because the systems are proprietary or because they involve not only \glspl{llm} but also external tools such as search \glspl{api} or code executors.\autocite{schick2024toolformer, karpas2022mrkl, yao2022react}
    Thus, a benchmark should not assume access to the raw model outputs but be able to operate on text completions.
    \item \emph{Probing capabilities beyond answering of \glspl{mcq}}. In real-world chemistry, as well as higher-level university education, multiple-choice questions are seldom utilized.
    Yet, most benchmarking frameworks focus on the \gls{mcq} setting because of the ease of evaluation. Realistic evaluations must measure capabilities beyond answering \gls{mcq}.
    \item \emph{Cover a diverse set of topics}. Chemistry, as the \enquote{central science}, bridges multiple disciplines.\autocite{Aspuru_Guzik_2018} To even just approximate \enquote{chemistry capabilities} the topics covered by a chemistry benchmark must be very diverse.
\end{itemize}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/flesch_kincaid_reading_ease.pdf}
    \caption{\textbf{Distribution of Flesch-Kincaid reading ease scores of the questions.} The Flesch-Kincaid reading ease score\autocite{flesch1948new} measures how easy a text is to read. It is calculated based on the average number of syllables per word and words per sentence. The higher the score, the easier the text is to read. The distribution of the questions' scores is shown in the histogram. }
    \label{fig:flesch_kincaid_reading_ease}
    \script{wordcloud.py}
\end{figure}

\Cref{fig:question_count_barplot_mcq_vs_general} shows that most questions in our corpus are \gls{mcq}.
A substantial fraction, in contrast to other benchmarks, is open-ended. 
\begin{figure}[htb]
    \centering
    \includegraphics{figures/question_count_barplot_mcq_vs_general.pdf}
    \caption{\textbf{Number of multiple choice questions vs.\ open-ended questions per topic.} The bar plot shows the number of \gls{mcq} and general questions per topic.}
    \label{fig:question_count_barplot_mcq_vs_general}
    \script{plot_statistics.py}
\end{figure}

The corpus of the questions in Chembench, as shown in \Cref{tab:chembench_corpus}, can be divided according to which topic they belong, or which type of knowledge is required in order to solve them correctly.

\begin{table*}[!t]
    \centering
        \caption{Summary of \chembench question types.}
    }
    \begin{tabular}{p{2.7cm}cp{10cm}}
        \toprule
        \textbf{Question Type} & \textbf{\%} & \textbf{Example Questions}  \\ 
        \midrule
        Chemical Preference & 35.0 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]N#Cc1ccc(OCCCN2CC3CN(CCNS(=O)(=O)c4ccc(F)cc4)CC(C2)O3)cc1[END_SMILES] \\
        & & B. [START_SMILES]O=C1CC(c2ccc(CC(NS(=O)(=O)c3cc(Cl)cc(Cl)c3)c3nc4ccccc4[nH]3)cc2)S(=O)(=O)N1[END_SMILES] \\
        \midrule
        Technical Chemistry & 1.5 & Which of the following statements is true about the different types of ideal reactors? \\
        & & A. In a batch reactor, the composition is uniformly mixed and remains the same throughout the reactor and at the exit \\
        & & B. In a batch reactor, the fluid passes through the reactor with no mixing of earlier and later entering fluid \\
        & & C. In a mixed flow reactor, the composition changes with time but is uniform everywhere within the reactor \\
        & & D. In a plug flow reactor, the fluid moves in single flow through the reactor with no mixing and no overtaking \\
        \midrule
        Organic Chemistry & 15.5 & What is the reaction mechanism that describes the following reaction (represented using reaction SMILES) [START_RXNSMILES]CCCl.CO[Na]>>[Na]Cl.CCOC[END_RXNSMILES]? \\
        & & A. $E_1$ \\
        & & B. $E_{cb}$ \\
        & & C. $S_N1$ \\
        & & D. $S_N2$ \\
        \midrule
        Toxicity/Safety & 24.2 & What details pertaining to a hazardous substance can be located on a Material Safety Data Sheet (MSDS)? \\
        & & A. All hazards regarding the material \\
        & & B. Physical and chemical properties \\
        & & C. Precautions for safe handling and storage \\
        \midrule
        Analytical Chemistry & 5.8 & Which of the following analytical methods is most appropriate for performing a survey analysis of a solid sample containing various metals? \\
        & & A. X-ray fluorescence analysis \\
        & & B. Differential pulse polarography \\
        & & C. Flame-atomic absorption spectroscopy \\
        & & D. Gas chromatography with flame ionization detector \\
        & & E. Hydride generation atomic absorption spectroscopy \\
        \midrule
        Materials Science & 3.1 & For NMR analysis, you need to digest the MOF in a strong acid to remove the linker and leave the metal clusters intact. Why would one choose \\ce{HF} over \\ce{HCl} for this purpose? \\
        & & A. \\ce{F-} forms a stable bonds to the metal ions \\
        & & B. \\ce{HF} has a better water solubility than \\ce{HCl} \\
        & & C. \\ce{HF} has a higher boiling point than \\ce{HCl} \\
        & & D. \\ce{HF} is a weaker acid than \\ce{HCl} \\
        \midrule
        General Chemistry & 5.3 & Which of the following salts is an acidic salt? \\
        & & A. \\ce{NH4Cl} \\
        & & B. \\ce{Na2CO3} \\
        & & C. \\ce{NaH2PO4} \\
        & & D. \\ce{Zn(OH)Cl} \\
        \midrule
        Physical Chemistry & 6.3 & The Born-Oppenheimer (BO) approximation is widely used in computational chemistry, but its accuracy can vary depending on the system. Among the following options, for which system is the Born-Oppenheimer approximation likely to be least applicable? \\
        & & A. \\ce{C60} \\
        & & B. \\ce{CH4} \\
        & & C. \\ce{Fe(CO)5} \\
        & & D. \\ce{H2+} \\
        & & E. \\ce{NaCl} \\
        \midrule
        Inorganic Chemistry & 3.3 & What is the oxidation number of the metal in the compound \\ce{[ZrF7]^{3-}}\\
        \toprule
        \textbf{Reasoning Type} & \textbf{Number of Questions} & \textbf{Example Question} \\
        \midrule
        Knowledge & 770 & Which of the following salts is an acidic salt? \\
        & & A. \\
        \midrule
        Reasoning & 825 & How can the optical impact of quantum confinement on the electronic structure of a quantum dot be observed experimentally? \\
        & & A. By measuring atomic force microscopy \\
        & & B. By measuring fourier transform infrared spectroscopy \\
        & & C. By measuring photoluminescence spectrum \\
        & & D. By measuring the absorption spectroscopy \\
        \midrule
        Intuition & 1001 & Imagine an early virtual screening campaign setting (accounting for simple aspects such as oral availability and small molecular profile, but no other modalities such as covalency or bifunctionality). Which of the following two candidates would you prefer for further development? \\
        & & A. [START_SMILES]CC1(C)Oc2ccc([N+](=O)[O-])cc2[C@@H](N2CCOCC2)[C@@H]1O[END_SMILES] \\
        & & B. [START_SMILES]Cc1ccccc1N=C(S)N1CCC(NC(=O)c2ccco2)CC1[END_SMILES] \\
        \midrule
        Calculation & 91 & Given that the average molar mass of the polymer chains in this sample of poly(lactic acid) (PLA) is \\pu{595 g mol^{-1}} using end-group analysis, where \\pu{0.1619 g} of PLA was dissolved in \\pu{25 cm^3} of benzyl alcohol and titrated with \\pu{0.0400 mol dm^{-3}} \\ce{KOH} solution. The volume of \\ce{KOH} solution required to reach the endpoint was \\pu{6.81 cm^3}. What is the average number of monomer units in each polymer chain of this sample? \\
        \bottomrule
    \end{tabular}
    \label{tab:chembench_corpus}
\end{table*}

@@

\subsection{Model performance}
We also evaluated the model performance on the entire \chembench corpus. 
\Cref{fig:barplot_all_correct_all_questions} shows the fraction of questions that were answered completely correctly by the models. 
Note that this ranking differs from the one on the \enquote{tiny} subset.

@@

\Cref{fig:parallel_coordinates_overall} shows this data as a parallel coordinates plot. 
This visualization highlights the critical observation that the ranking of the models highly depends on the questions they are evaluated on.
Only very broad benchmarks have the potential to provide a comprehensive view of a model's capabilities. However, even in those cases, the weighting of the different topics is crucial.
Hence, we believe that fine-grained analysis of model performance is vital for the development of future benchmarks.

\begin{figure}[htb]
    \centering
    \includegraphics{figures/parallel_coordinates_overall.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \chembench corpus.} The parallel coordinates plot shows the performance of the models on the different topics of the \chembench corpus. The performance is measured as the fraction of questions answered completely correctly by the models. }
    \label{fig:parallel_coordinates_overall}
    \script{make_parallel_coordinates_plot.py}
\end{figure}

\begin{figure}[htb]
    \centering
    \includegraphics{figures/parallel_coordinates_tiny.pdf}
    \caption{\textbf{Performance of the models on the different topics of the \enquote{tiny} subset.} The parallel coordinates plot shows the performance of the models on the different topics of the \enquote{tiny} subset. The performance is measured as the fraction of questions answered completely correctly by the models. }
    \label{fig:parallel_coordinates_tiny}
    \script{make_parallel_coordinates_plot.py}
\end{figure}

@@

\begin{figure}[htb]
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source.} The heatmap shows, in color, the fraction of questions answered completely correctly by different systems for some of our data sources. The performance is measured as the fraction of questions answered completely correctly by the models. A score of one (red) indicates that all questions were answered completely correctly, while a score of zero (blue) indicates that none of the questions were answered completely correctly.
        We see that the performance of the models varies significantly between the different data sources. For instance, it is interesting to observe that questions sourced based on textbooks seem easier for our leading models than for humans. However, this performance does not correlate with performance on other sources, e.g., semi-programmatically created tasks such as questions about the number of signals in an \gls{nmr} spectrum.
    }
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

One might wonder if questions that are more difficult to parse lead to worse performance of the models.
\Cref{fig:reading_ease_vs_model_performance} shows no clear correlation between the reading ease of the questions and the performance of the models.

\begin{figure}
    \centering
    \hspace*{-1cm}
    \includegraphics{figures/reading_ease_vs_model_performance.pdf}
    \caption{\textbf{Model performance as a function of reading ease.} The violin plots show the distribution of reading ease scores for questions answered completely correctly and those not. We do not observe a clear correlation between the reading ease of the questions and the performance of the models. }
    \script{reading_ease_vs_model_performance.py}
    \label{fig:reading_ease_vs_model_performance}
\end{figure}

In addition, we analyzed the performance on questions which requires calculation. For this, we manually labeled questions that require multiple calculation steps. 
We find that the ranking of models is different for questions with our without calculations (\Cref{fig:requires_cal}).

\begin{figure}
    \centering
    \includegraphics{figures/model_overall_cal.pdf}
    \caption{\textbf{Overall model performance for questions with and without calculation steps.} We find that the ranking of models changes if we evaluate them on questions that require and do not require calculations, respectively.}
    \script{requires_calculation_plot.py}
    \label{fig:requires_cal}
\end{figure}

@@

\begin{table}
    \caption{\textbf{Spearman correlation coefficients for the correlation of model performance with molecular features.} The table shows the Spearman correlation coefficient $\rho$ for the correlation of the performance of the models with the number of atoms and the complexity of the molecules. }
    \begin{tabularx}{\textwidth}{XXXX XXXX}
        \toprule
        topic & molecular descriptor & \(\rho\) GPT-4 & \(\rho \) Claude 3 & \( \rho \) Galactica &  \( \rho \) humans  \\ 
        \midrule
        number of \gls{nmr} signals & number of atoms &  \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_number_nmr_peaks.txt}  & \variable{output/correlation_correlation/spearman_num_atoms_human_is_number_nmr_peaks.txt} \\
                              & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_number_nmr_peaks.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_number_nmr_peaks.txt} \\
        \midrule 
        total electron counts & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_electron_counts.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_electron_counts.txt} \\
        \midrule 
        \gls{smiles} \gls{iupac} name matching & number of atoms & \variable{output/correlation_correlation/spearman_num_atoms_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_num_atoms_human_is_name.txt} \\
                & complexity & \variable{output/correlation_correlation/spearman_complexity_gpt4_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_claude3_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_galactica_120b_is_name.txt} & \variable{output/correlation_correlation/spearman_complexity_human_is_name.txt} \\
        \bottomrule
    \end{tabularx}
    \label{tab:correlation_coefficients}
\end{table}

\subsection{Influence of model scale}
To obtain first insights in how the performance \glspl{llm} depends on scale, we tested the \glspl{llm} of the LLaMA series. 
Interestingly, we find that the 7B and 70B models perform comparably, with the 13B showing lower performance (fraction of correct answers for the 7B, 13B, and 70B models are \variable{output/llama/llama_7b.txt}, \variable{output/llama/llama_13b.txt}, \variable{output/llama/llama_70b.txt}).

Note that such analyses are difficult as models are typically not directly comparable in terms of dataset and training protocol.\autocite{biderman2023pythia}

\subsection{Human baseline}
\paragraph{App} To facilitate the collection of responses, we developed a responsive web application in Typescript using the Next.js\autocite{nextjs} app router framework.
This application handles serving the user interface and exposes various \gls{rest} \glspl{api} for relevant operations.
We utilize a MySQL\autocite{mysql} database and Prisma \gls{orm}\autocite{prisma} for efficient database management.
The web application is styled with Tailwind CSS\autocite{tailwindcss} using the shadcn/ui component library and uses NextAuth\autocite{nextauth} for easy and secure user authentication and postMark for sending Emails.
The application is hosted on the Vercel web hosting platform.

@@

We also recorded the time humans took to answer the questions. This time is the time from the question being displayed to the human to the human submitting the answer.
Interestingly, we found no significant correlation between the experience of the human scorers and the performance on the questions (\Cref{fig:human_timing}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\)$\quad$, and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot, it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
    \label{fig:human_timing}
\end{figure}

Additionally, we prompted users to provide additional information about their experience in chemistry. 
While we recorded fine-grained information, e.g., their specialization, we focused on the number of years since the first university-level chemistry course.
\Cref{fig:experience_vs_correctness} shows that the experience of the human scorers was not significantly correlated with the correctness of their answers (\Cref{fig:experience_vs_correctness}, Spearman's \(\rho \approx \variable{output/spearman_experience_score.txt}\)$\quad$, and \(p \approx \variable{output/spearman_experience_score_p.txt}\)).

\begin{figure}[htb]
    \centering
    \includegraphics{figures/experience_vs_correctness.pdf}
    \script{analyze_human_data.py}
    \caption{\textbf{Experience of human  scorers vs.\ correctness of their answers.} The experience (in the number of years since the first university-level chemistry course) of the human scorers was not significantly correlated with the correctness of their answers.}
    \label{fig:experience_vs_correctness}
\end{figure}

@@

\begin{figure}[htb] 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The bar plots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}
